Group 9 Presentation

### 2021-12-08 SVM.Rmd
Everything is working, presentation html file generated.

>>>>

{r SVM}

train <- read.csv("train.csv")
test <- read.csv("test.csv")

train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)

SVM_radial = svm(HeartDisease~., data=train, kernel="radial", gamma=0.25, cost=0.4)

preds = predict(SVM_radial, test, type="class")
acc = sum(ifelse(preds == test$HeartDisease, 1, 0))/nrow(test)

table(preds,test$HeartDisease)

overall_SVM <- acc

paste("The overall fraction of correct predictions in the test dataset is :", acc)

### 2021-12-08 presentation.Rmd
Everything is working, presentation html file generated.

+ ST_Slope during exercise:

@@

# MSE values to use:
paste("Tuning Lambda",best_lambda_lasso)
#lasso_MSE
paste("Number of zeros",num_zeros)

@@

```{r SVM}

SVM_radial = svm(HeartDisease~., data=train, kernel="radial", gamma=0.25, cost=0.4)

preds = predict(SVM_radial, test, type="class")
acc = sum(ifelse(preds == test$HeartDisease, 1, 0))/nrow(test)

table(preds,test$HeartDisease)

overall_SVM <- acc

paste("The overall fraction of correct predictions in the test dataset is :", acc)
```

@@

```{r}
library(knitr)
df1 = data.frame(Method = c("Logistic Regression","LDA","KNN","LASSO","Bagging","Random Forest","Boosting","SVM"),  MSE = c(overall_logit,overall_LDA,overall_knn_1,overall_lasso,overall_bag,overall_RF,overall_boost,overall_SVM))

>>>>

+ ST_Slope (Slope of the peak exercise ST segment):

@@

# MSE values to use:
paste("Tuning Lambda",best_lambda_lasso)
#lasso_MSE
#paste("Number of zeros",num_zeros)

@@

```{r Data, include=FALSE}
heart_train = read.csv("train.csv")

heart_train$Sex = factor(heart_train$Sex)
heart_train$ChestPainType = factor(heart_train$ChestPainType)
heart_train$FastingBS = factor(heart_train$FastingBS)
heart_train$RestingECG = factor(heart_train$RestingECG)
heart_train$ExerciseAngina = factor(heart_train$ExerciseAngina)
heart_train$ST_Slope = factor(heart_train$ST_Slope)
heart_train$HeartDisease = factor(heart_train$HeartDisease)
```

```{r SVM_Linear}
# Train a Linear SVM and find the best cost value
# We set scale=TRUE becuase the continuous varibles seem to be normally distrabuted (from EDA)
svm_linear_cv = tune(svm, HeartDisease~., scale=TRUE, kernel="linear", data=heart_train,
                      ranges = list(cost = seq(0.1, 5, by = 0.1)))
svm_linear = svm_linear_cv$best.model

preds = predict(svm_linear, heart_train, type="class")

```{r SVM_Polynomial}
# Train a Polynomial SVM
# Find the best cost and degree parameter
svm_poly_cv = tune(svm, HeartDisease~., scale=TRUE, kernel="polynomial", data=heart_train,
                      ranges = list(cost = seq(0.1, 5, by = 0.1),
                                    degree = c(2,3,4, 5)))
svm_poly = svm_poly_cv$best.model

preds = predict(svm_poly, heart_train, type="class")

```{r SVM_Radial}
# Train a Radial SVM
# Find the best cost and gamma parameter
svm_radial_cv = tune(svm, HeartDisease~., scale=TRUE, kernel="radial", data=heart_train,
                      ranges = list(cost = seq(0.2, 5, by = 0.2),
                                    gamma = seq(0.25, 3, by = 0.25)))
svm_radial = svm_radial_cv$best.model

preds = predict(svm_radial, heart_train, type="class")

```{r Testing}
heart_test = read.csv("test.csv")

preds_liner = predict(svm_linear, heart_test, type="class")
acc_liner = sum(ifelse(preds_liner == heart_test$HeartDisease, 1, 0))/nrow(heart_test)

preds_poly = predict(svm_poly, heart_test, type="class")
acc_poly = sum(ifelse(preds_poly == heart_test$HeartDisease, 1, 0))/nrow(heart_test)

preds_radial = predict(svm_radial, heart_test, type="class")
acc_radial = sum(ifelse(preds_radial == heart_test$HeartDisease, 1, 0))/nrow(heart_test) #87.2%

c("Linear Svm" = acc_liner, "Polynomial Svm" = acc_poly, "Radial SVM" = acc_radial)
```

- Confusion Matrix for Radial:

```{r Best_SVM}
table(heart_test$HeartDisease, preds_radial)
overall_SVM <- acc_radial
```

@@

```{r}
library(knitr)
df1 = data.frame(Method = c("Logistic Regression","LDA","KNN","LASSO","Bagging","Random Forest","Boosting","SVM"),  Overall_Correct_Pred.= c(overall_logit,overall_LDA,overall_knn_1,overall_lasso,overall_bag,overall_RF,overall_boost,overall_SVM))
